Using Semantic Similarity to Assist Assessing MCR Comment Usefulness

### 2014-07-27 sections/introduction.tex
update more introduction... continuing early morning tomorrow.

\noindent In addition to addressing the research questions above, the main contributions of this paper are:
\dan{these are more "results" than contributions.... need to reword this!}
\begin{itemize}
\item A practical to apply approach to mine natural text of comments in code reviews and classify their usefulness based on VSM similarity.
\item The experimental results show that the approach can classify comments with an F$_1$ score of 0.681 and 0.693.
\item We found that 85\% of comments in Gerrit are automatically generated and not likely useful (but important for record keeping). For the remaining 15\%, about 43\% of them are automatically classified as useful, while about 34\% are classified as not useful. The remaining 23\% are undetermined and require manual classification. Thus the classification effort is reduced by about 77\%.
\item xx\% of the comments did not have unanimity (i.e. unclear), and of these yy\% were automatically determined to be useful or not useful. Follow up with dissenting assessors found mis-judgement occurred zz\% of the time whereby in retrospect the comment would have had unanimity. This indicates the method is useful in identifying subjective judgement errors. 
\item Of the 23\% not automatically classified (i.e. undetermined), qq\% were unclear. Of the (1-qq)\% with unanimity, followup with assessors found in retrospect they would change their assessment making the comment unclear. This indicates the method is useful in identifying chance unanimity errors or group think bias.
\end{itemize} 
%Software Inspection is basically composed of a three-step procedure: preparation, inspection meeting, and repair.

>>>>

\noindent In addition to addressing the research questions above, the main contributions of this paper are:
\dan{these are more "results" than contributions.... need to reword this!}
\begin{itemize}
\item A practical approach to mine natural text of comments in code reviews and classify their usefulness based on VSM similarity.
\item The experimental results, which show that the approach can classify comments with an F$_1$ score of 0.681 and 0.693.
\item We found that 85\% of comments in Gerrit are automatically generated and not likely useful (but important for record keeping). For the remaining 15\%, about 43\% of them are automatically classified as useful, while about 34\% are classified as not useful. The remaining 23\% are undetermined and require manual classification. Thus the classification effort is reduced by about 77\%.
\item \TODO{xx}\% of the comments did not have unanimity (i.e. unclear), and of these \TODO{yy}\% were automatically determined to be useful or not useful. Follow up with dissenting assessors found mis-judgement occurred \TODO{zz}\% of the time whereby in retrospect the comment would have had unanimity. This indicates the method is useful in identifying subjective judgement errors. 
\item Of the 23\% not automatically classified (i.e. undetermined), \TODO{qq}\% were unclear. Of the \TODO{(1-qq)}\% with unanimity, followup with assessors found in retrospect they would change their assessment making the comment unclear. This indicates the method is useful in identifying chance unanimity errors or group think bias.
\end{itemize} 
%Software Inspection is basically composed of a three-step procedure: preparation, inspection meeting, and repair.
